A Generalized Sphere Theorem for Positively Curved Combinatorial 3-Manifolds

### 2013-04-14 paper/paper.tex
more writing

\section{Basic Stuff}
\label{sect:basics}

@@

We are now finally able to state our main result, which shows that any positively curved 3-manifold with diameter larger than half that allowed by Corollary \ref{thm:discrete_BM_expanded_paths}.

@@

\noindent The proof of this result relies on a complete census of positively curved combinatorial 3-manifolds completed by Lutz and Sullivan. The census contains 4787 manifolds and contains examples of the 3-sphere $S^3$, the real projective space $\mathbb{RP}^3$, the lens spaces $L(3,1)$ and $L(4,1)$ and the cube space $S^3/Q$. The creation of such a census is a highly non-trivial task, for details see \cite{LutzSul}.

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.6\linewidth]{figures/global_statistics.png}
    \caption{Global statistics}
    \end{center}
    \label{global_statistics}
\end{figure}

@@

>>>>

\section{Preliminaries}
\label{sect:basics}

@@

We are now able to state our main result.

@@

\noindent The proof of this theorem relies on a complete census of positively curved combinatorial 3-manifolds completed by Lutz and Sullivan. The census contains 4787 manifolds, with the following topologies represented: the 3-sphere $S^3$, the real projective space $\mathbb{RP}^3$, the lens spaces $L(3,1)$ and $L(4,1)$ and the cube space $S^3/Q$. The creation of such a census is a highly non-trivial task, for details see \cite{LutzSul}.

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.6\linewidth]{figures/global_statistics.png}
    \caption{Global statistics. TO DO: Change diameter labels to $1, H, 2, J, 3, 2H, 4, 2J$ and put these on horizontal axis. TO DO: Change graph to show separate data points for each topological type. }
    \end{center}
    \label{global_statistics}
\end{figure}

@@

TO DO: Give a brief description of the algorithm used.

\section{Discussion}

TO DO: Discuss the big picture stuff concerning adding possible PL paths between vertices. Mention the benefits of hops and jumps not mentioned here (unique continuation of minimal paths)

We should mention another notable advantage of expanding the space of paths to include hops and edges. In classical differential geometry, the starting point, the initial direction, and length completely determine a geodesic. There is no branching of geodesics. This property of fundamental importance to many proofs in Riemannian geometry. If we use only edge-paths, then in a positively curved combinatorial 3-manifold it is possible to have two minimal paths with the same length and which begin by traversing the same edge, yet reach distinct destination vertices. That is, using only edge paths, minimal geodesics can ``branch''.

This important property is restored if we include hops and edges. In \cite{Trout10} the following is shown.

\begin{thm}
\end{thm}
